### 2013-03-14 au_topology_seminar_talk_2013_02_18.tex
Added readme, working on ZFC example for k-Markov result in LFKP

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

\usepackage{graphicx}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\newcommand{\oneptcomp}[1]{#1^*}

\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}

\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\newcommand{\rest}{\restriction}

\newcommand{\largecomment}[1]{}

@@

We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}.

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not the union of countably-many point-finite collections.
\end{theorem}

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindel\"of, but not $\sigma$-metacompact.

Let $X = Y^2$, and let $\mathcal{V}$ be an open cover of $X$ by $2^\omega$ clopen sets. Since $Y^2 \setminus \Delta$ is metalindel\"of and $\Delta$ is compact, let $\mathcal{V}'$ be a refinement of $\mathcal{U}$ such that it is a point-countable cover of $Y^2 \setminus \Delta$, and let $\mathcal{V}''$ be a refinement of $\mathcal{U}$ such that it is finite cover of $\Delta$. Then $\mathcal{U} = \mathcal{V}'\cup\mathcal{V}''$ is point-countable on $Y^2$, and if it was the union of countably-many point-finite collections, so would $\mathcal{V}'$ (making $Y^2\setminus \Delta$ $\sigma$-metacompact, contradiction).
\end{proof}

@@

\begin{proof}
Let $x\in X$. $C^x = \{c \in C : x \in U_c\}$ is a countable collection by the point-countability of $\mathcal{U}$, so label its elements as $\{c^x_n: n<\omega\}$.

@@

Recall that $\mathcal{U}$ is not the union of the countably-many point-finite collections, and 
  \[
    \mathcal{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
  \]
so we may choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.

@@

>>>>

\input{./header.tex}

@@

We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}. We require a slight modification of a result of Gruenhage and Michael \cite{Michael}:

\begin{theorem}\label{michael}
Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base of cardinality $\kappa$ for $X$. Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ of cardinality $\kappa$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
\end{theorem}

\begin{proof}
asdf?
\end{proof}

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mc{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
\end{theorem}

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. (See Todercevic \cite{Todercevic} for an example.) It follows by \cite{G1} that $Y^2$ is hereditarily metaLindel\"of, but not hereditarily $\sigma$-metacompact. Let $X$ be a non-$\sigma$-metacompact subset of $Y^2$, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.

Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.  Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.
\end{proof}

@@

\begin{proof}
Let $x\in X$. $C^x = \{c \in C : x \in U_c\}$ is a countable collection by the point-countability of $\mc{U}$, so label its elements as $\{c^x_n: n<\omega\}$.

@@

Recall that $\mc{U}$ is not the union of the countably-many point-finite collections, and 
  \[
    \mc{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
  \]
so we may choose $n$ where $\mc{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mc{U}_n$.

@@

\bibitem{Michael}
  G. Gruenhage and E. Michael, 
  \emph{A result on shrinkable open covers}.
  Proceedings of the 1983 topology conference (Houston, Tex., 1983), 1983, pp. 37–43.

\bibitem{Todercevic}
  S. Todercevic,
  \emph{Trees and linearly ordered sets}.
  Handbook of Set-theoretic Topology (North-Holland, Amsterdam, 1984), pp. 235-293
